Our Future Nuclear Data Needs

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Added missing references, cleaned up a few things

\usepackage[american]{babel}
% \usepackage{amsmath}
\usepackage[version=3]{mhchem} 
% % \usepackage{fixltx2e}
% % \usepackage{refcount}
\usepackage{siunitx}
% % \usepackage{lastpage}
% % \usepackage{textcomp}
% \usepackage{mathtools}
% 
% \usepackage{xfrac}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
% % \usepackage{cool}
% % \usepackage{cancel}
\usepackage{microtype}
% \usepackage{listings}
% % \usepackage{mcode}
\usepackage [autostyle, english = american]{csquotes}
% % \usepackage{longtable}
% % \usepackage{subcaption}
% \usepackage{booktabs,siunitx}
% \usepackage{gensymb}
% \usepackage[normalem]{ulem}

@@

\hyphenation{gamma-rays}

@@

@@

For fission theory, we can make a distinction in practice between description of the fission process up to scission (pre-scission physics), and the events that follow scission (post-scission physics). Eventually, one could envision a comprehensive model that accurately follows the entire fission process from the formation of the parent nucleus to the last decays of the final product nuclei within a single internally consistent theoretical framework. Such a model is not yet feasible so different physics models are used to treat pre- and post-scission processes. A wide range of theoretical approaches have been developed since the late 1930's to describe pre-scission physics, including scission-point models \cite{Wil76,Lem15}, microscopic-macroscopic models \cite{Mol15} with random-walk dynamics \cite{Wa17}, Langevin dynamics \cite{Sie17}, Time-dependent Hartree-Fock and Hartree-Fock-Bogoliubov theory \cite{Koo76,Neg78,Tan15,God16}, the time-dependent superfluid local density approximation \cite{Ste11,Bul13,Ste15,Bul16}, and the time-dependent generator-coordinate method \cite{Ber91,Gou05,Rei16}.Several models have also been developed to describe post-scission physics and built into computer codes, such as GEF \cite{Sch16}, FIFRELIN \cite{Lit15}, CGMF \cite{Tal14}, and FREYA \cite{Ran09,Ver18}.

@@

In addition to standard experiments looking at individual fission properties, multi-parameter measurements that give a comprehensive view of a fission event should be pursued as facilities and detectors improve. Ideally, a multi-parameter experiment would record all possible fission observables (e.g., fragment charge, mass, and energy distributions as well as neutron and gamma spectra and multiplicities) on an event-by-event basis, thereby making it possible to reconstruct the state of the nucleus at scission. In practice, each additional observable reduces statistics, making such measurements exceedingly challenging. Finally, there are experimental measurements that directly probe the pre-scission dynamics of the fission process, although they carry large uncertainties and suffer from various ambiguities and limitations. These include measurements of scission neutrons \cite{Pe09}, fission time scales \cite{Jac09}, and muon-induced fission \cite{Mar80}. Probes of pre-scission physics can provide unique insights into the details of the fission process, and are therefore extremely valuable to fission theory.

@@

\subsection{Improved \ce{^{235,238}U} and \ce{^{239}Pu}(n,n') data for neutron transport}\label{sec:n_transport}

@@

CIELO has relatively little energy or angle differential data to draw upon to aid in its evaluation of (n,n') on the \enquote{Big 3} Actinides, leading to \enquote{significant differences amongst the evaluations for \ce{^{239}Pu} in the fast energy range, with ENDF/B-VII.1 and JENDL-4.0 lying significantly above the JEFF-3.1 evaluation.} \cite{Cha14}.  The \ce{^{239}Pu} data referenced in their paper are all from indirect measurements made prior to 1970 \cite{Bat69, And61}.  The case is similar for \ce{^{235}U} where they note that differences for $E_n >$ 50 keV \enquote{have a large impact on the fast criticality (Godiva), leading to a 540 pcm swing in calculated criticality, as shown by Go Chiba \cite{Chi12}.}

@@

The antineutrino spectrum produced in a nuclear reactor is calculated as the sum of the spectra produced by each of the nuclear fuels, \ce{^{235,238}U} and \ce{^{239,241}Pu}, weighted by the respective fission fractions \cite{Vog81}.   The spectra for each fuel can be calculated using nuclear databases, in what is commonly known as the \enquote{summation method}.   Alternatively, for \ce{^{235}U} and \ce{^{239,241}Pu}, the spectra can also be calculated by converting the aggregate electron spectra measured at ILL in the 1980s \cite{Fel82,Sch85,Hah89}.   The current best predictions for  \ce{^{235}U} and \ce{^{239,241}Pu} are those by Huber \cite{Hub11} using the conversion method, while for \ce{^{238}U} is that by Mueller et al. \cite{Mue11} using a hybrid conversion-summation method.

The use of nuclear databases to calculate antineutrino spectra is considered less precise than the conversion method due to deficiencies in the underlying fission and decay data, such as beta intensities \cite{20}, beta shape factors due to first-forbidden transitions \cite{Hay14}, evaluated libraries issues \cite{Son15} and fission yields \cite{Son16}.   There have been considerable efforts in the last few years to improve this situation, including (i) experimental campaigns in Jyvaskyla \cite{Alg10}, ORNL \cite{Ras16} and ANL \cite{MccTBD} to obtain highly precise values of beta intensities, which have been incorporated in the ENDF/B-VIII.0 decay data sub-library; (ii) measurements of isomeric ratios in ILL, Jyvaskyla and ANL; (iii) measurements of fission yields in GELINA \cite{Viv00}, GSI \cite{Pel17} and LANL \cite{Duk16}; (iv) a recent IAEA Coordinated Research Project on beta-delayed neutron emitters \cite{DimXX} that would improve the derivation of cumulative fission yields from independent ones.   Also planned are measurements of beta shape factors as well as a new IAEA Coordinated Research Project to evaluate fission yields.
Another issue affecting the summation method is the lack of fission yield correlation matrices in the evaluated fission data libraries.   As a result, uncertainties cannot be fully computed.  There has been some progress in this area, for instance, the ongoing OECD-NEA subgroup 44 will incorporate this topic \cite{SobXX}.

@@

These experiments would involve a sample of depleted \ce{^{238}U} since recent results from IBD indicate that the contribution to the observed anomaly in the antineutrino experiment can be attributed to issues with the \ce{^{238}U}(n,f) yields. These measurements could be performed at the Godiva in the same fashion as the \ce{^{235}U} irradiation used to validate FIER, or other well-documented fast neutron facilities including the thick target deuteron break neutron source at the LBNL 88-Inch cyclotron \cite{Harrig2018} and the High Flux Neutron Generator at UC-Berkeley \cite{All18} and compare the results to the FIER predictions to inform both the fission yield and decay data for \ce{^{238}U}(n,f).

\subsection{Improved (n,x$\gamma$) data for active interrogation}

@@

The interpretation of this data requires detailed knowledge of both the double-differential neutron scattering and gamma-ray production cross sections from fast down to thermal neutron energies.  The Evaluated Gamma Activation File \cite{Fir14} provides partial gamma-ray cross section data for transitions between discrete states following thermal neutron capture.  At higher energies the Atlas of Gamma-rays from the Scattering of Reactor Fast Neutrons \cite{Dem78}, which has recently been compiled into a database and reconciled to reflect state-of-the-art gamma-ray energies from ENSDF \cite{Hur18}, offers discrete gamma-ray cross sections for irradiation with fast fission neutrons.

@@

>>>>

\usepackage[american]{babel}
% \usepackage{amsmath}
\usepackage[version=3]{mhchem} 
% % \usepackage{fixltx2e}
% % \usepackage{refcount}
\usepackage{siunitx}
% % \usepackage{lastpage}
% % \usepackage{textcomp}
% \usepackage{mathtools}
% 
% \usepackage{xfrac}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
% % \usepackage{cool}
% % \usepackage{cancel}
% \usepackage{microtype}
% \usepackage{listings}
% % \usepackage{mcode}
\usepackage [autostyle, english = american]{csquotes}
% % \usepackage{longtable}
% % \usepackage{subcaption}
% \usepackage{booktabs,siunitx}
% \usepackage{gensymb}
% \usepackage[normalem]{ulem}

@@

\hyphenation{gamma-rays}
\hyphenation{Spec-tro-met-ers}

@@

% Remove overfull hbox warnings in bibliography
\usepackage{etoolbox}
\apptocmd{\sloppy}{\vbadness 10000\relax}{}{}
% \emergencystretch=1em

\pdfminorversion=7

@@

For fission theory, we can make a distinction in practice between description of the fission process up to scission (pre-scission physics), and the events that follow scission (post-scission physics). Eventually, one could envision a comprehensive model that accurately follows the entire fission process from the formation of the parent nucleus to the last decays of the final product nuclei within a single internally consistent theoretical framework. Such a model is not yet feasible so different physics models are used to treat pre- and post-scission processes. A wide range of theoretical approaches have been developed since the late 1930's to describe pre-scission physics, including scission-point models \cite{Wil76,Lem15}, microscopic-macroscopic models \cite{Mol15} with random-walk dynamics \cite{War17}, Langevin dynamics \cite{Sie17}, Time-dependent Hartree-Fock and Hartree-Fock-Bogoliubov theory \cite{Koo76,Neg78,Tan15,God16}, the time-dependent superfluid local density approximation \cite{Ste11,Bul13,Ste15,Bul16}, and the time-dependent generator-coordinate method \cite{Ber91,Gou05,Rei16}.Several models have also been developed to describe post-scission physics and built into computer codes, such as GEF \cite{Schm16}, FIFRELIN \cite{Lit15}, CGMF \cite{Tal14}, and FREYA \cite{Ran09,Ver18}.

@@

In addition to standard experiments looking at individual fission properties, multi-parameter measurements that give a comprehensive view of a fission event should be pursued as facilities and detectors improve. Ideally, a multi-parameter experiment would record all possible fission observables (e.g., fragment charge, mass, and energy distributions as well as neutron and gamma spectra and multiplicities) on an event-by-event basis, thereby making it possible to reconstruct the state of the nucleus at scission. In practice, each additional observable reduces statistics, making such measurements exceedingly challenging. Finally, there are experimental measurements that directly probe the pre-scission dynamics of the fission process, although they carry large uncertainties and suffer from various ambiguities and limitations. These include measurements of scission neutrons \cite{Petrov2009}, fission time scales \cite{Jac09}, and muon-induced fission \cite{Mar80}. Probes of pre-scission physics can provide unique insights into the details of the fission process, and are therefore extremely valuable to fission theory.

@@

\subsection{Improved \texorpdfstring{\ce{^{235,238}U}}{235,238U} and \texorpdfstring{\ce{^{239}Pu}}{239Pu}(n,n') data for neutron transport}\label{sec:n_transport}

@@

CIELO has relatively little energy or angle differential data to draw upon to aid in its evaluation of (n,n') on the \enquote{Big 3} Actinides, leading to \enquote{significant differences amongst the evaluations for \ce{^{239}Pu} in the fast energy range, with ENDF/B-VII.1 and JENDL-4.0 lying significantly above the JEFF-3.1 evaluation.} \cite{Cha14}.  The \ce{^{239}Pu} data referenced in their paper are all from indirect measurements made prior to 1970 \cite{Batchelor1969, Andreev1961}.  The case is similar for \ce{^{235}U} where they note that differences for $E_n >$ 50 keV \enquote{have a large impact on the fast criticality (Godiva), leading to a 540 pcm swing in calculated criticality, as shown by Go Chiba \cite{Chi12}.}

@@

The antineutrino spectrum produced in a nuclear reactor is calculated as the sum of the spectra produced by each of the nuclear fuels, \ce{^{235,238}U} and \ce{^{239,241}Pu}, weighted by the respective fission fractions \cite{Vog81}.   The spectra for each fuel can be calculated using nuclear databases, in what is commonly known as the \enquote{summation method}.   Alternatively, for \ce{^{235}U} and \ce{^{239,241}Pu}, the spectra can also be calculated by converting the aggregate electron spectra measured at ILL in the 1980s \cite{Fei82,Sch85,Hah89}.   The current best predictions for  \ce{^{235}U} and \ce{^{239,241}Pu} are those by Huber \cite{Hub11} using the conversion method, while for \ce{^{238}U} is that by Mueller et al. \cite{Mue11} using a hybrid conversion-summation method.

The use of nuclear databases to calculate antineutrino spectra is considered less precise than the conversion method due to deficiencies in the underlying fission and decay data, such as beta intensities \cite{Fal12}, beta shape factors due to first-forbidden transitions \cite{Hay14}, evaluated libraries issues \cite{Son15} and fission yields \cite{Son16}.   There have been considerable efforts in the last few years to improve this situation, including (i) experimental campaigns in Jyvaskyla \cite{Alg10}, ORNL \cite{Ras16} and ANL \cite{MccTBD} to obtain highly precise values of beta intensities, which have been incorporated in the ENDF/B-VIII.0 decay data sub-library; (ii) measurements of isomeric ratios in ILL, Jyvaskyla and ANL; (iii) measurements of fission yields in GELINA \cite{Viv00}, GSI \cite{Pel17} and LANL \cite{Duk16}; (iv) a recent IAEA Coordinated Research Project on beta-delayed neutron emitters \cite{DimXX} that would improve the derivation of cumulative fission yields from independent ones.   Also planned are measurements of beta shape factors as well as a new IAEA Coordinated Research Project to evaluate fission yields.
Another issue affecting the summation method is the lack of fission yield correlation matrices in the evaluated fission data libraries.   As a result, uncertainties cannot be fully computed.  There has been some progress in this area, for instance, the ongoing OECD-NEA subgroup 44 will incorporate this topic \cite{SobXX}.

@@

These experiments would involve a sample of depleted \ce{^{238}U} since recent results from IBD indicate that the contribution to the observed anomaly in the antineutrino experiment can be attributed to issues with the \ce{^{238}U}(n,f) yields. These measurements could be performed at the Godiva in the same fashion as the \ce{^{235}U} irradiation used to validate FIER, or other well-documented fast neutron facilities including the thick target deuteron break neutron source at the LBNL 88-Inch cyclotron \cite{Harrig2018} and the High Flux Neutron Generator at UC-Berkeley \cite{ayllon2018design} and compare the results to the FIER predictions to inform both the fission yield and decay data for \ce{^{238}U}(n,f).

\subsection{Improved (n,x\texorpdfstring{$\gamma$}{ gamma}) data for active interrogation}

@@

The interpretation of this data requires detailed knowledge of both the double-differential neutron scattering and gamma-ray production cross sections from fast down to thermal neutron energies.  The Evaluated Gamma Activation File \cite{Fir15} provides partial gamma-ray cross section data for transitions between discrete states following thermal neutron capture.  At higher energies the Atlas of Gamma-rays from the Scattering of Reactor Fast Neutrons \cite{Dem78}, which has recently been compiled into a database and reconciled to reflect state-of-the-art gamma-ray energies from ENSDF \cite{Hur18}, offers discrete gamma-ray cross sections for irradiation with fast fission neutrons.

@@

\emergencystretch=2em
